---
title: "Pulkit's Dashboard On Online Sales Data"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    social: [ "twitter", "facebook", "menu"]
    source_code: embed
---

```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)
library(DT)
library(rpivotTable)
library(ggplot2)
library(plotly)
library(dplyr)
library(openintro)
library(highcharter)
library(ggvis)
library(gridExtra)
```

```{r}
data <-read.csv("C:\\Users\\PULKIT\\Downloads\\Details.csv")
```

# Data Visualization On online Shopping

## Row

### Online Shopping Analysis

```{r}
valueBox(paste("Online Shopping"),
         color = "purple")
```

### Online Shopping Users

```{r}
valueBox(paste("1500"),
         icon = "fa-user"
         ,color = "purple")
```

### **Total Sales All time**

```{r}
gauge(round(sum(data$Amount),
            digits = 5),
            min = 0,
            max = 500000,
            gaugeSectors(success = c(0, 10000),
                         warning = c(10000, 100000),
                         danger = c(100000, 1000000),
                         colors = c("green", "yellow", "darkgreen")))
```
### **Average profit per order**
```{r}
gauge(round(mean(data$Profit),
            digits = 3),
            min = 0,
            max = 100,
            gaugeSectors(success = c(0, 20),
                         warning = c(20, 50),
                         danger = c(50, 100),
                         colors = c("green", "yellow", "darkgreen")))
```

### Electronic

```{r}
category_counts_electronic <- sum(data$Category == "Electronics")
valueBox(category_counts_electronic, 
         icon = "bolt",
         color = "#800080")

```

### Furniture

```{r}
# Count occurrences of "Furniture" in the "Category" column
category_counts <- sum(data$Category == "Furniture")

# Print the count using valueBox
valueBox(category_counts, 
         icon = "couch", 
         color = "purple")
         #width = 4)


```

### Clothing

```{r}
# Count occurrences of "Electronic" in the "Category" column
category_counts_clothing <- sum(data$Category == "Clothing")

# Print the count using valueBox with an electricity icon
valueBox(category_counts_clothing, 
         icon = "tshirt",
         color = "purple")

```

Row
-----------------------------

### Total Amount of Sales According to the Category and Sub-Category

```{r}

# Define colors for each category
category_colors <- c("Furniture" = "#FFA500", "Electronics" = "#FF5733", "Clothing" = "#800080")

# Arrange the data by category and sub-category
data <- arrange(data, Category, Sub.Category)

# Create a plot
p1 <- data %>%
  group_by(Category, Sub.Category) %>%
  summarise(Profit = sum(Amount)) %>%
  plot_ly(x = ~Sub.Category,
          y = ~Profit,
          color = ~Category,
          colors = category_colors,  # Use the defined colors
          type = 'bar') %>%
  layout(xaxis = list(title = "Sub-Categories"),
         yaxis = list(title = 'Total Amount'),
         barmode = 'stack')#,  # Stack bars for each sub-category
        # width = 800,        # Set the width
        # height = 800)       # Set the height

p1
```

### Payment methods used by customer

```{r}
p2 <- data %>%
         group_by(PaymentMode) %>%
         summarise(count = n()) %>%
         filter(count>50) %>%
         plot_ly(labels = ~PaymentMode,
                 values = ~count,
                 marker = list(colors =  c("#87CEEB", "#FF7F50", "#90EE90", "#DA70D6","#FFD700"))) %>%
         add_pie(hole = 0) %>%
         layout(xaxis = list(zeroline = F,
                             showline = F,
                             showticklabels = F,
                             showgrid = F),
                yaxis = list(zeroline = F,
                             showline = F,
                             showticklabels=F,
                             showgrid=F))
p2
```

# Profit Analysis By per Order_id
### Total Profit per order

```{r}
profit_by_order <- aggregate(Profit ~ Order.ID, data = data, FUN = sum)

# Create a scatter plot
scatter_plot <- plot_ly(profit_by_order,
                        x = ~Order.ID,
                        y = ~Profit,
                        type = "scatter",
                        mode = "markers",
                        marker = list(color = "blue", opacity = 0.7),
                        text = paste("Order ID:", profit_by_order$OrderID,
                                     "<br>Total Profit:", profit_by_order$Profit),
                        hoverinfo = "text") %>%
                layout(xaxis = list(title = "Order ID"),
                       yaxis = list(title = "Total Profit"),
                       title = "Total Profit by Order ID Scatter Plot")

scatter_plot

```

# Shopping data of states
### Scatter Plot of States and total Orders

```{r}
state_counts <- table(data$State)

# Convert state counts to a data frame
state_counts_df <- data.frame(State = names(state_counts),
                              Count = as.numeric(state_counts),
                              stringsAsFactors = FALSE)

# Arrange states by count in ascending order
state_counts_df <- state_counts_df[order(state_counts_df$Count), ]

# Create a box plot
box_plot <- plot_ly(state_counts_df,
                    x = ~State,
                    y = ~Count,
                    type = "bar",
                    marker = list(color = "blue"),
                    text = paste("State:", state_counts_df$State,
                                 "<br>Count:", state_counts_df$Count),
                    hoverinfo = "text") %>%
            layout(xaxis = list(title = "State"),
                   yaxis = list(title = "Count"),
                   title = "Box Plot of Order Count by State")

box_plot

```


# Map

### Map

```{r}
order<-data %>%
  group_by(State)%>%
  summarise(total=n())
highchart()%>%
  hc_title(text="Analysis")%>%
  hc_subtitle(text="Source: Data")%>%
  hc_add_series_map(usgeojson,order,
                    name="State",
                    value="total",
                    joinBy=c("woename","State"))%>%
  hc_mapNavigation(enabled = TRUE)
```


# Pivot Table

```{r}
rpivotTable(data,
            aggregatorName = "Count",
            cols= "Quantity",
            rows = "State",
            rendererName = "Table")
```

# Data Table
```{r}
datatable(data,
          caption = "Online Shopping Data",
          rownames = T,
          filter = "top",
          options = list(pageLength = 25))
```